---
title: "Course Project"
author: "Land"
date: "03/20/2015"
output: html_document
---


##Clean the data

Get rid of columns which contain NA value or it's a empty slot. 

```{r, cache=TRUE}
library(dplyr)
training <- read.csv("training.csv")
training[training == ""] <- NA
#put NA value in some empty slot. 
varsa <- nrow(training) - sum(training$new_window == "yes")
training <- training[,colSums(is.na(training)) < varsa]
#get rid of columns whose na is more than numbers of total rows minus number of 
#window.
```
```{r, results='hide'}
head(training)
str(training)
summary(training)
```
After some exploratory analysis, the variables: num_window", "new_window", "cvtd_timestamp", "raw_timestamp_part_1", "raw_timestamp_part_2", "X", and  "user_name" are excluded.

```{r}
varsb <- c("num_window", "new_window", "cvtd_timestamp", 
           "raw_timestamp_part_1", "raw_timestamp_part_2", "X", "user_name")
training <- select(training, -one_of(varsb))
#get rid of columns whose name is...
```

##Building model, Cross Validation

After reading the reference, I decided to use random forest to build the model. 
I only specify the ntree is 50. the use cross validation (5 fold) instead of the default, Bootstrapped.

```{r, cache=TRUE}
library(caret)
set.seed(998)
inTrain <- createDataPartition(y=training$classe, p=0.6,list=FALSE)
smallT <- training[inTrain,]
#rm(inTrain,training, varsa,varsb)
#release memory space.
```
```{r}
#modFit <- train(classe ~ ., data=smallT, method="rf",trControl=trainControl(method="cv",number=5), prox=TRUE, ntree=50)
modFit <- readRDS("RFmodel_cross_validated.rds")
```

Because the limited memory of my computer, I can't knit the HTML file and
build the model at the same time, so I have to build the model first, save it 
as "RFmodel_cross_validated.rds". You can see the parameters I use to build the
model above.

The result is like this:

```{r, cache=TRUE}
modFit
```

The Accuracy is 0.9865.
```{r, cache=TRUE}
modFit$finalModel
```


##Check the result, Out of Sample Error

```{r, cache=TRUE}
testing <- training[-inTrain,]
pred <- predict(modFit, testing)
table(pred, testing$classe)
```
you can see the prediction result is pretty good from the table.

```{r, cache=TRUE}
realtesting <- read.csv("testing.csv")
predr <- predict(modFit, realtesting)
```

The 20 tests need to be submited are:
```{r}
predr
```

##Reference

Velloso, E.; Bulling, A.; Gellersen, H.; Ugulino, W.; Fuks, H. Qualitative Activity Recognition of Weight Lifting Exercises. Proceedings of 4th 
International Conference in Cooperation with SIGCHI (Augmented Human '13) . Stuttgart, Germany: ACM SIGCHI, 2013. 
